Deciding to Disclose

### 2015-06-04 Model.tex
Bayes eg final
Fix eqn endings
Added CPT eg

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) &= -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) &= -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) &= -10
\end{align}
\end{equation}

@@

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
R_{w}(l, l) &= -10
\end{align}
\end{equation}

@@

>>>>

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) &= -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) &= -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) &= -10
\end{align*}
\end{equation*}

@@

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
R_{w}(l, l) &= -10
\end{align*}
\end{equation*}

@@

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j)p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.

\begin{equation*}
\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
v(u_{w}) &= f(u_{w}) &= u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} &= 7.59\\
w^{+}(p(l)p(r | l))  &= \frac{(p(l)p(r | l))^\gamma}{[(p(l)p(r | l))^\gamma + (1-(p(l)p(r | l)))^\gamma]^\frac{1}{\gamma}}\\
w^{+}(p(l)p(r | l))  &= \frac{\frac{1}{24}^{0.61}}{[\frac{1}{24}^{0.61} + (1-\frac{1}{24})^{0.61}]^\frac{1}{0.61}} &= 0.12\\
w^{+}(p(l)p(n | l)) &= \frac{\frac{1}{8}^{0.61}}{[\frac{1}{8}^{0.61} + (1-\frac{1}{8})^{0.61}]^\frac{1}{0.61}} &= 0.21\\
w^{+}(p(m)p(r | l)) &= 0.12
w^{+}(p(m)p(n | l)) &= 0.21
w^{+}(p(h)p(r | l)) &= 0.24
w^{+}(p(h)p(n | l)) &= 0.42
V(l) &= 0.12\cdot7.59 + 0.21\cdot7.59 + 0.12\cdot7.59 + 0.21\cdot7.59 + 0.24\cdot7.59 + 0.42\cdot7.59 &= 10.02
\end{align*}
\end{equation*}
